---
output: html_document
---

# K-48 Retirement Funds Statistical Re-Weighting
## Summary Report
### `r paste0(format(Sys.time(), '%d %B %Y'))`

### Results
#### Total Assets


```{r, warning = F, message = F, echo = F,}

cmff_fin5 %>%
  ungroup() %>%
  group_by(period) %>%
  summarise(orig = sum(tot, na.rm = T)/10^9,
            revised = sum(tst, na.rm = T)/10^9) %>%
  gather(key,tot,orig:revised) %>%
  ggplot(aes(x = period, y = tot, group = key, fill = key)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "",
       y = "R billions")


```

#### Total Liabilities

```{r, warning = F, message = F, echo = F,}

cmff_finliab5 %>%
  ungroup() %>%
  group_by(period) %>%
  summarise(orig = sum(tot, na.rm = T)/10^9,
            revised = sum(tst, na.rm = T)/10^9) %>%
  gather(key,tot,orig:revised) %>%
  ggplot(aes(x = period, y = tot, group = key, fill = key)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "",
       y = "R billions")


```

#### Total Assets by Fund Classification

```{r, warning = F, message = F, echo = F, fig.height = 10, fig.width = 10}

cmff_fin5 %>%
  ungroup() %>%
  group_by(period, fund_class) %>%
  summarise(orig = sum(tot, na.rm = T)/10^9,
            revised = sum(tst, na.rm = T)/10^9) %>%
  gather(key,tot,orig:revised) %>%
  ggplot(aes(x = period, y = tot, group = key, fill = key)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "",
       y = "R billions") +
  facet_wrap(.~fund_class, scale = "free", ncol = 1)


```

#### Total Liabilities by Fund Classification

```{r, warning = F, message = F, echo = F, fig.height = 10, fig.width = 10}

cmff_finliab5 %>%
  ungroup() %>%
  group_by(period, fund_class) %>%
  summarise(orig = sum(tot, na.rm = T)/10^9,
            revised = sum(tst, na.rm = T)/10^9) %>%
  gather(key,tot,orig:revised) %>%
  ggplot(aes(x = period, y = tot, group = key, fill = key)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "",
       y = "R billions") +
  facet_wrap(.~fund_class, scale = "free", ncol = 1)


```

#### Total Assets by FSCA Category

```{r, warning = F, message = F, echo = F, fig.height = 30, fig.width = 20}

cmff_fin5 %>%
  ungroup() %>%
  group_by(period, fsca_item) %>%
  summarise(orig = sum(tot, na.rm = T)/10^9,
            revised = sum(tst, na.rm = T)/10^9) %>%
  gather(key,tot,orig:revised) %>%
  ggplot(aes(x = period, y = tot, group = key, fill = key)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "",
       y = "R billions") +
  facet_wrap(.~fsca_item, scale = "free", ncol = 2)


```

#### Total Liabilities by FSCA Category

```{r, warning = F, message = F, echo = F, fig.height = 25, fig.width = 20}

cmff_finliab5 %>%
  ungroup() %>%
  group_by(period, fsca_item) %>%
  summarise(orig = sum(tot, na.rm = T)/10^9,
            revised = sum(tst, na.rm = T)/10^9) %>%
  gather(key,tot,orig:revised) %>%
  ggplot(aes(x = period, y = tot, group = key, fill = key)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "",
       y = "R billions") +
  facet_wrap(.~fsca_item, scale = "free", ncol = 2)


```

#### Total Assets by FSCA Category and Type

```{r, warning = F, message = F, echo = F, fig.height = 30, fig.width = 20}

cmff_fin5 %>%
  ungroup() %>%
  group_by(period, fsca_item, type) %>%
  summarise(orig = sum(tot, na.rm = T)/10^9,
            revised = sum(tst, na.rm = T)/10^9) %>%
  gather(key,tot,orig:revised) %>%
  ggplot(aes(x = period, y = tot, group = key, fill = key)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "",
       y = "R billions") +
  facet_wrap(.~fsca_item+type, scale = "free", ncol = 2)


```

#### Total Assets by Fund Classification and FSCA Category

```{r, warning = F, message = F, echo = F, fig.height = 60, fig.width = 20}

cmff_fin5 %>%
  ungroup() %>%
  group_by(period, fund_class, fsca_item) %>%
  summarise(orig = sum(tot, na.rm = T)/10^6,
            revised = sum(tst, na.rm = T)/10^6) %>%
  gather(key,tot,orig:revised) %>%
  ggplot(aes(x = period, y = tot, group = key, fill = key)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "",
       y = "R millions") +
  facet_wrap(.~fund_class+fsca_item, scale = "free", ncol = 2)


```

#### Total Liabilities by Fund Classification and FSCA Category

```{r, warning = F, message = F, echo = F, fig.height = 40, fig.width = 20}

cmff_finliab5 %>%
  ungroup() %>%
  group_by(period, fund_class, fsca_item) %>%
  summarise(orig = sum(tot, na.rm = T)/10^6,
            revised = sum(tst, na.rm = T)/10^6) %>%
  gather(key,tot,orig:revised) %>%
  ggplot(aes(x = period, y = tot, group = key, fill = key)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "",
       y = "R millions") +
  facet_wrap(.~fund_class+fsca_item, scale = "free", ncol = 2)


```

#### Total Assets by Fund Classification and FSCA Category and Item

```{r, warning = F, message = F, echo = F, fig.height = 160, fig.width = 20}

cmff_fin5 %>%
  ungroup() %>%
  group_by(period, fund_class, fsca_item, item.x) %>%
  summarise(orig = sum(tot, na.rm = T)/10^6,
            revised = sum(tst, na.rm = T)/10^6) %>%
  gather(key,tot,orig:revised) %>%
  ggplot(aes(x = period, y = tot, group = key, fill = key)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "",
       y = "R millions") +
  facet_wrap(.~fund_class+fsca_item+item.x, scale = "free", ncol = 3)


```

#### Total Liabilities by Fund Classification and FSCA Category and Item

```{r, warning = F, message = F, echo = F, fig.height = 60, fig.width = 20}

cmff_finliab5 %>%
  ungroup() %>%
  group_by(period, fund_class, fsca_item, item.x) %>%
  summarise(orig = sum(tot, na.rm = T)/10^6,
            revised = sum(tst, na.rm = T)/10^6) %>%
  gather(key,tot,orig:revised) %>%
  ggplot(aes(x = period, y = tot, group = key, fill = key)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "",
       y = "R millions") +
  facet_wrap(.~fund_class+fsca_item+item.x, scale = "free", ncol = 2)


```