---
output: html_document
---

# K-48 Retirement Funds Statistical Re-Weighting
## Summary Report: Income Statement
### `r paste0(format(Sys.time(), '%d %B %Y'))`

### Results
#### Total Income Minus Expenditure (Net)


```{r, warning = F, message = F, echo = F}

cmff_is_det_prop3 %>%
    ungroup() %>%
    group_by(period) %>%
    summarise(tot = sum(tst, na.rm = T)/10^9) %>%
  #gather(key,tot,orig:tot) %>%
  ggplot(aes(x = period, y = tot)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "",
       y = "R billions") 

```

#### Total Income Minus Expenditure (Net) Per Fund Class

```{r, warning = F, message = F, echo = F, fig.width= 10}

cmff_is_det_prop3 %>%
    ungroup() %>%
    group_by(period, fund_class) %>%
    summarise(tot = sum(tst, na.rm = T)/10^9) %>%
  #gather(key,tot,orig:tot) %>%
  ggplot(aes(x = period, y = tot)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "",
       y = "R billions") +
  facet_wrap(.~fund_class, scales = "free")


```

#### Income and Expenditure High Level Categories

```{r, warning = F, message = F, echo = F, fig.height = 10, fig.width = 9, fig.height = 12}

cmff_is_det_prop3 %>%
    ungroup() %>%
    group_by(period, k48_class_agg) %>%
    summarise(tot = sum(tst, na.rm = T)/10^9) %>%
  #gather(key,tot,orig:tot) %>%
  ggplot(aes(x = period, y = tot)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "",
       y = "R billions") +
  facet_wrap(.~k48_class_agg, scales = "free", ncol = 2)


```

#### Income and Expenditure Lower Level Categories

```{r, warning = F, message = F, echo = F, fig.height = 20, fig.width = 9}

cmff_is_det_prop3 %>%
    ungroup() %>%
    group_by(period, k48_class) %>%
    summarise(tot = sum(tst, na.rm = T)/10^9) %>%
  #gather(key,tot,orig:tot) %>%
  ggplot(aes(x = period, y = tot)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "",
       y = "R billions") +
  facet_wrap(.~k48_class, scales = "free", ncol = 2)


```

#### Income and Expenditure By Item

```{r, warning = F, message = F, echo = F, fig.height = 60, fig.width = 9}

cmff_is_det_prop3 %>%
    ungroup() %>%
    group_by(period, item) %>%
    summarise(tot = sum(tst, na.rm = T)/10^9) %>%
  #gather(key,tot,orig:tot) %>%
  ggplot(aes(x = period, y = tot)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "",
       y = "R billions") +
  facet_wrap(.~item, scales = "free", ncol = 2)


```

#### Income and Expenditure by Fund Class and Aggregate Categories

```{r, warning = F, message = F, echo = F, fig.height = 40, fig.width = 9}

cmff_is_det_prop3 %>%
    ungroup() %>%
    group_by(period, fund_class,k48_class_agg) %>%
    summarise(tot = sum(tst, na.rm = T)/10^9) %>%
  #gather(key,tot,orig:tot) %>%
  ggplot(aes(x = period, y = tot)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "",
       y = "R billions") +
  facet_wrap(.~fund_class+k48_class_agg, scales = "free", ncol = 2)


```

#### Income and Expenditure Per Fund Class and Low Level Categories

```{r, warning = F, message = F, echo = F, fig.height = 70, fig.width = 9}

cmff_is_det_prop3 %>%
    ungroup() %>%
    group_by(period, fund_class, k48_class) %>%
    summarise(tot = sum(tst, na.rm = T)/10^9) %>%
  #gather(key,tot,orig:tot) %>%
  ggplot(aes(x = period, y = tot)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "",
       y = "R billions") +
  facet_wrap(.~fund_class+k48_class, scales = "free", ncol = 2)


```

#### Income and Expenditure by Fund Class and Item

```{r, warning = F, message = F, echo = F, fig.height = 170, fig.width = 9}

cmff_is_det_prop3 %>%
    ungroup() %>%
    group_by(period, fund_class, item) %>%
    summarise(tot = sum(tst, na.rm = T)/10^9) %>%
  #gather(key,tot,orig:tot) %>%
  ggplot(aes(x = period, y = tot)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme(legend.position = "top",
        legend.title = element_blank()) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "",
       y = "R billions") +
  facet_wrap(.~fund_class+item, scales = "free", ncol = 2)


```

